---
title: "Lab 01 - Redux"
format: html
author: Ted Galanthay
editor: visual
fig-width: 7
fig-height: 5
---

## Loading packages

```{r}
library(tidyverse) 
library(datasauRus)
```

## Answering questions

1.  Datasaurus Dozen hase 1846 rows and 3 variables.

Let's make a frequency table:

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

Let's plot the dino dataset. First, we copy the data into dino_data.

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
```

Then, we plot it.

```{r}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

ROAR!!

Let's look at the correlation coefficient.

```{r}
dino_data %>% summarize(r = cor(x, y))
```

Now we'll look at the star dataset.

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
dino_data %>% summarize(r = cor(x, y))
```

3.  The correlation coefficient for the star data is slightly larger (-0.0629611 versus -0.6447185) than for the dinosaur data.

Now we'll repeat this for the circle data.

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And ... the correlation coefficient is

```{r}
dino_data %>% summarize(r = cor(x, y))
```

4.  The correlation coefficient for the circle data is slightly less, -0.06834336, than that for the dinosaur data, -0.6447185.

Let's plot all datasets at once:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

And we can get the correlation coefficients for all the data by grouping, using group_by():

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

We can change the figure width and height by adding to the YAML at the top of our Quarto document.
