---
title: "Lab 01 - Redux"
format: html
author: Ted Galanthay
editor: visual
---

## Loading packages

```{r}
library(tidyverse) 
library(datasauRus)
```

## Answering questions

1.  Datasaurus Dozen hase 1846 rows and 3 variables.

Let's make a frequency table:

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

Let's plot the dino dataset. First, we copy the data into dino_data.

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
```

Then, we plot it.

```{r}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

ROAR!!

Let's look at the correlation coefficient.

```{r}
dino_data %>% summarize(r = cor(x, y))
```

Now we'll look at the star dataset.

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
dino_data %>% summarize(r = cor(x, y))
```

3.  The correlation coefficient for the star data is slightly larger (-0.0629611 versus -0.6447185) than for the dinosaur data.
